---
title: "FACEBOOK use analysis"
author: '[Rui Pei](https://www.asc.upenn.edu/people/rui-pei)'
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---
```{r setup, warning=FALSE}
rm(list = ls())
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(ggpubr))
suppressPackageStartupMessages(library(pander))
suppressPackageStartupMessages(library(jtools))
# suppressPackageStartupMessages(library(stringr))
# suppressPackageStartupMessages(library(broom.mixed))
# suppressPackageStartupMessages(library(sjPlot))
# suppressPackageStartupMessages(library(huxtable))
# suppressPackageStartupMessages(library(ggstance))
```

```{r defineFunctions, warning=FALSE}
pd <- position_dodge(0.3) # move them .05 to the left and right

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
numericcharacters <- function(x) {
  !any(is.na(suppressWarnings(as.numeric(x)))) & is.character(x)
}

scale1 <- function(x) scale(x)[,1]

construct_coef_df = function(dvs,df){
  fhab_mds = lapply(dvs, function(x) {
    lm(substitute(i ~ fhab + study_t + scanner_t, list(i = as.name(x))), data = df)
})
  fhab_sums = lapply(fhab_mds, summary)

  femo_mds = lapply(dvs, function(x) {
      lm(substitute(i ~ femo + study_t + scanner_t, list(i = as.name(x))), data = df)
  })
  femo_sums = lapply(femo_mds, summary)
  
  fhab_betas = c()
  femo_betas = c()
  fhab_se = c()
  femo_se = c()
  for (i in c(1:length(dvs))){
    fhab_betas = c(fhab_betas,fhab_sums[[i]]$coefficients[2,1])
    femo_betas = c(femo_betas,femo_sums[[i]]$coefficients[2,1] )
    fhab_se = c(fhab_se, fhab_sums[[i]]$coefficients[2,2])
    femo_se = c(femo_se, femo_sums[[i]]$coefficients[2,2])
  }
  
  coef_df = data.frame("IV" = c(rep("Habitual FB use", length(dvs)), rep("Emotional FB use", length(dvs))),
                       "DV" = c(dvs,dvs),
                       "beta" = c(fhab_betas, femo_betas),
                       "se" = c(fhab_se, femo_se))
  coef_df = coef_df %>%
  mutate(IV = factor(coef_df$IV, levels=c("Habitual FB use", "Emotional FB use")))
  return(coef_df)
}

plot_coef_df = function(coef_dv){
  g1 = ggplot(coef_df, aes(x=DV, y=beta, colour=IV)) + 
    geom_errorbar(aes(ymin= beta-1.96*se, ymax= beta+1.96*se), width=.1, position=pd) +
    geom_point(position=pd) + theme_pubr() + 
  scale_color_manual(values = c("Habitual FB use" = "dodgerblue", "Emotional FB use" = "forestgreen")) +
   geom_hline(yintercept=0, linetype="dashed", 
                color = "grey", size=1) + 
  rotate_x_text(45)
  return(g1)
}

construct_coef_df_iri = function(dvs,df){
  mds1 = lapply(dvs, function(x) {
    lm(substitute(i ~ IRI_Perspective_Taking + study_t + scanner_t, list(i = as.name(x))), data = df)
})
  sums1 = lapply(mds1, summary)
  
  mds2 = lapply(dvs, function(x) {
    lm(substitute(i ~ IRI_Fantasy + study_t + scanner_t, list(i = as.name(x))), data = df)
})
  sums2 = lapply(mds2, summary)
  
  mds3 = lapply(dvs, function(x) {
    lm(substitute(i ~ IRI_Empathic_Concern + study_t + scanner_t, list(i = as.name(x))), data = df)
})
  sums3 = lapply(mds3, summary)
  
  mds4 = lapply(dvs, function(x) {
    lm(substitute(i ~ IRI_Personal_Distress + study_t + scanner_t, list(i = as.name(x))), data = df)
})
  sums4 = lapply(mds4, summary)

  betas1 = c()
  betas2 = c()
  betas3 = c()
  betas4 = c()
  se1 = c()
  se2 = c()
  se3 = c()
  se4 = c()
  for (i in c(1:length(dvs))){
    betas1 = c(betas1,sums1[[i]]$coefficients[2,1])
    betas2 = c(betas2,sums2[[i]]$coefficients[2,1])
    betas3 = c(betas3,sums3[[i]]$coefficients[2,1])
    betas4 = c(betas4,sums4[[i]]$coefficients[2,1])
    se1 = c(se1, sums1[[i]]$coefficients[2,2])
    se2 = c(se2, sums2[[i]]$coefficients[2,2])
    se3 = c(se3, sums3[[i]]$coefficients[2,2])
    se4 = c(se4, sums4[[i]]$coefficients[2,2])
  }
  
  coef_df = data.frame("IV" = c(rep("Perspective taking", length(dvs)),
                                rep("Fantasy", length(dvs)),
                                rep("Empathic concern", length(dvs)),
                                rep("Personal distress", length(dvs))),
                       "DV" = c(dvs,dvs,dvs,dvs),
                       "beta" = c(betas1, betas2,betas3,betas4),
                       "se" = c(se1, se2,se3,se4))
  coef_df = coef_df
  return(coef_df)
}

plot_coef_iri = function(coef_dv){
  g1 = ggplot(coef_df, aes(x=DV, y=beta, colour=IV)) + 
    geom_errorbar(aes(ymin= beta-1.96*se, ymax= beta+1.96*se), width=.1, position=pd) +
    geom_point(position=pd) + theme_pubr()  +
   geom_hline(yintercept=0, linetype="dashed", 
                color = "grey", size=1) + 
  rotate_x_text(45)
  return(g1)
}

corstar <- function(x, y = NULL, use = "pairwise", method = "pearson", round = 3, row.labels, col.labels, ...) {
  
  require(psych)

  ct <- corr.test(x, y, use, method)    # calculate correlation
  r <- ct$r                             # get correlation coefs
  p <- ct$p                             # get p-values

  stars <- ifelse(p < .001, "***", ifelse(p < .01, "** ", ifelse(p < .05, "*  ", "   "))) # generate significance stars
  
  m <- matrix(NA, nrow = nrow(r) * 2, ncol = ncol(r) + 1) # create empty matrix

  rlab <- if(missing(row.labels)) rownames(r) else row.labels # add row labels
  clab <- if(missing(col.labels)) {
    if(is.null(colnames(r)))
      deparse(substitute(y))
    else
      colnames(r)
  } else {
    col.labels # add column labels
  }
  
  rows <- 1:nrow(m)                     # row indices
  cols <- 2:ncol(m)                     # column indices
  
  odd <- rows %% 2 == 1                 # odd rows
  even <- rows %% 2 == 0                # even rows
  m[odd, 1] <- rlab                     # add variable names
  m[even, 1] <- rep("", sum(even))      # add blank
  
  m[odd, cols] <- paste(format(round(r, round), nsmall = round, ...), stars, sep = "")     # add r coefs
  m[even, cols] <- paste("(", format(round(p, round), nsmall = round, ...), ")", sep = "") # add p-values
  
  colnames(m) <- c(" ", clab)           # add colnames
  m                                     # return matrix
}
```


```{r importWideData, warning = FALSE, message = FALSE}
path =  "~/Box Sync/CurrentProjects_Penn/TPS12_BART/99_fomo/github/"
setwd(path)
## socialMedia data
socialMedia = read.csv(paste0(path, '0_facebook/tps2_facebook.csv'),na.strings=c("","NA"), stringsAsFactors = FALSE)[-1,] 

socialMedia = socialMedia %>% 
  mutate(TPS_ID = as.factor(TPS_ID)) %>%
  mutate_if(is.character,as.numeric) %>%
  mutate(fhab = rowMeans(.[,10:19], na.rm = FALSE),
         femo = rowMeans(.[c(8,9,20:39)], na.rm = FALSE), ## include the two "feel connected" questions in Emotional FB use.
         TPS_ID = as.character(TPS_ID)) %>%
  select(TPS_ID, fhab, femo)

cyber = read.csv(paste0(path, '0_cyberball/cyberball_roi.csv'), stringsAsFactors = FALSE) 

age = read.csv(paste0(path, '0_surveys/tps12_scanner_study_age.csv'), stringsAsFactors = FALSE) %>%
  select(TPS_ID, age, study_t, scanner_t)



iri = read.csv(paste0(path, '0_surveys/iri_tps12.csv'), stringsAsFactors = FALSE)
iri = iri %>%
  mutate(IRI_mean = rowMeans(select(iri, starts_with("IRI_")), na.rm = FALSE))


nts = read.csv(paste0(path, '0_surveys/nts.csv'), stringsAsFactors = FALSE)

df = cyber %>%
  left_join(socialMedia, by = "TPS_ID") %>%
  left_join(age, by = "TPS_ID") %>%
  left_join(iri, by = "TPS_ID") %>%
  left_join(nts, by = "TPS_ID") 


# Remove NAs
df = df %>% drop_na(age,fhab,femo, NTS_Belongingness,
                    NTS_SelfEsteem, NTS_Control,
                    NTS_MeaningfulExistence, study_t, scanner_t,
                    IRI_Perspective_Taking, IRI_Fantasy, 
                    IRI_Empathic_Concern, IRI_Personal_Distress)
```

# 1. Participants

We include `r dim(df)[1]` participants in this report. 

# 2. Data description{.tabset}

## Habitual FB use. 

1 - Strongly disagree 
7 - Strongly agree

1. Using Facebook is something I do automatically.	
2. Using Facebook is something I do without meaning to do it.	
3. Using Facebook is something I do without thinking.	
4. Using Facebook is something I start doing before I realize I'm doing it.
5. Using Facebook is something that would require effort not to do it.
6. Using Facebook is something I do without having to consciously remember.
7. Using Facebook is something that belongs to my daily routine.	
8. Using Facebook is something I would find hard not to do.	
9. Using Facebook is something I have no need to think about doing.	
10. Using Facebook is something that's typically "me".

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "fhab",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```

## Emotional FB use. 

1. I feel connected to my friends when I use Facebook.
2. I feel connected to my family members when I use Facebook.	

I get an urge to post on Facebook from my computer or phone the moment when ...
3. something makes me feel amused	
4. something makes me feel surprised
5. something makes me feel awed
6. something makes me feel loved
7. something makes me feel proud	
8. something makes me feel excited	
9. something makes me feel grateful	
10. something makes me feel happy	
11. something makes me feel inspired	
12. something makes me feel confident	
13. something makes me feel angry	
14. something makes me feel nervous	
15. something makes me feel awkward	
16. something makes me feel stressed	
17. something makes me feel jealous	
18. something makes me feel lonely	
19. something makes me feel scared	
20. something makes me feel upset	
21. something makes me feel ashamed	
22. something makes me feel guilty

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "femo",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```



## ROIS

Scrit to obtain the ROI values at [jupyter hub](https://fmrisrv2.asc.upenn.edu/user/rpei@asc.upenn.edu/notebooks/socialMedia/SPM_firstLevelModel/extract_ROIs_vijayakumar_rois_20200127.ipynb#).



```{r fig.width=2, fig.height = 1}
roi_names = colnames(df)[c(3:20,23)]
source = c("functional ROI",
           "functional ROI",
           "functional ROI",
           "functional ROI",
           "Dufour et al., 2013","Dufour et al., 2013","Dufour et al., 2013",
           "Dufour et al., 2013","Dufour et al., 2013","Dufour et al., 2013",
           "Dufour et al., 2013",
           "Vijayakumar et al., 2017","Vijayakumar et al., 2017",
           "Vijayakumar et al., 2017","Vijayakumar et al., 2017",
           "Vijayakumar et al., 2017","Vijayakumar et al., 2017",
           "Vijayakumar et al., 2017","Vijayakumar et al., 2017")
img_folder = '/Users/Rui/Box Sync/CurrentProjects_Penn/TPS12_BART/99_fomo/data/cyberball/ROIs/png/'
imgs = paste0(img_folder, roi_names, '.png')

rois = data.frame("name" = roi_names, "source" = source, "image" = imgs)


rois %>% 
  mutate(
    image %>% pander::pandoc.image.return()
    ) %>% 
  select(-image) %>%
  pander()
```

## IRI

__Perspective taking__

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "IRI_Perspective_Taking",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```

__Perspective taking__

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "IRI_Personal_Distress",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```

__Empathic concern__

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "IRI_Empathic_Concern",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```

__Fantasy__

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "IRI_Fantasy",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```

## Need threat scale

__Lower scores indicate greater distress__

__Belongingness__

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "NTS_Belongingness",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```

__Self esteem__

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "NTS_SelfEsteem",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```

__Control__

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "NTS_Control",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```

__MeaningfulExistence__

```{r fig.width=3, fig.height = 1.5}
ggdensity(df, x = "NTS_MeaningfulExistence",
   add = "mean", rug = TRUE,
   color = "study_t", fill = "study_t")
```

# 3. Correlation matrix (IRI + NTS)

```{r message = FALSE, warning = FALSE}
m = corstar(df[,c("IRI_Perspective_Taking","IRI_Fantasy",
              "IRI_Empathic_Concern","IRI_Personal_Distress",
              "NTS_Belongingness","NTS_SelfEsteem",
              "NTS_Control","NTS_MeaningfulExistence")])

m[c(1,2),2] = ""
m[c(1:4),3] = ""
m[c(1:6),4] = ""
m[c(1:8),5] = ""
m[c(1:10),6] = ""
m[c(1:12),7] = ""
m[c(1:14),8] = ""

df_m = as.data.frame(m[,1:8])
rownames(df_m) = NULL
kable(df_m) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```


# 4. Linking FB use with self-report{.tabset}

```{r}
# ## scale the IVs and DVs
# df = df %>%
#   mutate_at(c(3:26,29:37), scale1)
```

## IRI

```{r}
dvs = c("IRI_Perspective_Taking","IRI_Fantasy",
                   "IRI_Empathic_Concern","IRI_Personal_Distress", "IRI_mean")

coef_df = construct_coef_df(dvs, df) %>%
  mutate(DV = gsub("IRI_", "", DV))

plot_coef_df(coef_dv)
```

## NTS

```{r}
dvs = c("NTS_Belongingness","NTS_SelfEsteem",
        "NTS_Control", "NTS_MeaningfulExistence","NTS_Mean")

coef_df = construct_coef_df(dvs, df) %>%
  mutate(DV = gsub("NTS_", "", DV))
plot_coef_df(coef_dv)
```


# 5. Linking FB use with neural data{.tabset}

## Functional ROIS

```{r}
dvs = c("subacc_roi_mask","rInsula_roi_mask",
        "lInsula_roi_mask", "functional_combined_roi_mask")

coef_df = construct_coef_df(dvs, df) %>%
  mutate(DV = gsub("_roi_mask", "", DV))
plot_coef_df(coef_dv)
```

## Dufour mentalzing meta-analytic ROIS

```{r}
dvs = c("vmpfc_roi_mask","dmpfc_roi_mask","mmpfc_roi_mask", "precuneus_roi_mask",            "lTpj_roi_mask","rTpj_roi_mask" ,"rSts_roi_mask",
        "saxe_combined_mask")

coef_df = construct_coef_df(dvs, df) %>%
  mutate(DV = gsub("_roi_mask", "", DV))
plot_coef_df(coef_dv)

md = lm(saxe_combined_mask ~ fhab +age + study_t + scanner_t, data = df)
summ(md, digits = 3) 

ggscatter(df, "fhab", "dmpfc_roi_mask")
```

## Neurosynth mentalzing ROIS

```{r}
df = df %>%
  dplyr::rename(.,neurosynth_mask = ns_ment_mask,
                ns_RSTS = ns_ment_clust1_mask,
                ns_RTPJ = ns_ment_clust2_mask,
                ns_DMPFC = ns_ment_clust3_mask,
                ns_PCC = ns_ment_clust4_mask,
                ns_VMPFC = ns_ment_clust5_mask,
                ns_hippocampus = ns_ment_clust6_mask,
                ns_LTPJ = ns_ment_clust7_mask,
                ns_LSTS = ns_ment_clust8_mask)
dvs = c("neurosynth_mask","ns_RSTS", "ns_RTPJ", 
        "ns_DMPFC","ns_PCC" ,"ns_VMPFC",
        "ns_hippocampus","ns_LTPJ","ns_LSTS")

coef_df = construct_coef_df(dvs, df) %>%
  mutate(DV = gsub("_mask", "", DV))
plot_coef_df(coef_dv)

md = lm(neurosynth_mask ~ fhab + age + study_t + scanner_t, data = df)
summ(md, digits = 3) 

ggscatter(df, "fhab", "neurosynth_mask")
```

## Vijayakumar social exclusion meta-analytic ROIs

```{r}
dvs = c("adult_lIFG_mask","adult_vACC_mask",
        "adult_posteriorCingulate_mask","adult_precuneus_mask",
        "adult_precentralGyrus_mask" ,
        "ado_lateralOFC_mask", "ado_vs_mask")

coef_df = construct_coef_df(dvs, df) %>%
  mutate(DV = gsub("_mask", "", DV))
plot_coef_df(coef_dv)
```

## dACC ROIS

```{r}
dvs = c("rotge_dacc1_mask","rotge_dacc2_mask",
        "dACC_anatomical")

coef_df = construct_coef_df(dvs, df) %>%
  mutate(DV = gsub("_mask", "", DV))
plot_coef_df(coef_dv)

# md = lm(dACC_anatomical_mask ~ femo + age + study_t + scanner_t, data = df)
# summary(md)
```

# 6. Link between neural activation in mentalizing regions and IRI{.tabset}

##  Dufour et al. meta-analytic regions



```{r}
dvs = c("vmpfc_roi_mask","dmpfc_roi_mask","mmpfc_roi_mask", "precuneus_roi_mask",            "lTpj_roi_mask","rTpj_roi_mask" ,"rSts_roi_mask",
        "saxe_combined_mask")

coef_df = construct_coef_df_iri(dvs, df) %>%
  mutate(DV = gsub("_roi_mask", "", DV))
plot_coef_iri(coef_dv)

md = lm(saxe_combined_mask ~ IRI_Fantasy + age + study_t + scanner_t, data = df)
summ(md) 
```

##  Neurosynth regions

```{r}
dvs = c("neurosynth_mask","ns_RSTS", "ns_RTPJ", 
        "ns_DMPFC","ns_PCC" ,"ns_VMPFC",
        "ns_hippocampus","ns_LTPJ","ns_LSTS")

coef_df = construct_coef_df_iri(dvs, df) %>%
  mutate(DV = gsub("_roi_mask", "", DV))
plot_coef_iri(coef_dv)

md = lm(neurosynth_mask ~ IRI_Fantasy + age + study_t + scanner_t, data = df)
summ(md) 
```

# 7. Link between neural activation in cyberball and NTS{.tabset}

```{r}
## function
construct_coef_df_nts = function(dvs,df){
  mds1 = lapply(dvs, function(x) {
    lm(substitute(i ~ NTS_Belongingness + study_t + scanner_t, list(i = as.name(x))), data = df)
})
  sums1 = lapply(mds1, summary)
  
  mds2 = lapply(dvs, function(x) {
    lm(substitute(i ~ NTS_SelfEsteem + study_t + scanner_t, list(i = as.name(x))), data = df)
})
  sums2 = lapply(mds2, summary)
  
  mds3 = lapply(dvs, function(x) {
    lm(substitute(i ~ NTS_Control + study_t + scanner_t, list(i = as.name(x))), data = df)
})
  sums3 = lapply(mds3, summary)
  
  mds4 = lapply(dvs, function(x) {
    lm(substitute(i ~ NTS_MeaningfulExistence + study_t + scanner_t, list(i = as.name(x))), data = df)
})
  sums4 = lapply(mds4, summary)

  betas1 = c()
  betas2 = c()
  betas3 = c()
  betas4 = c()
  se1 = c()
  se2 = c()
  se3 = c()
  se4 = c()
  for (i in c(1:length(dvs))){
    betas1 = c(betas1,sums1[[i]]$coefficients[2,1])
    betas2 = c(betas2,sums2[[i]]$coefficients[2,1])
    betas3 = c(betas3,sums3[[i]]$coefficients[2,1])
    betas4 = c(betas4,sums4[[i]]$coefficients[2,1])
    se1 = c(se1, sums1[[i]]$coefficients[2,2])
    se2 = c(se2, sums2[[i]]$coefficients[2,2])
    se3 = c(se3, sums3[[i]]$coefficients[2,2])
    se4 = c(se4, sums4[[i]]$coefficients[2,2])
  }
  
  coef_df = data.frame("IV" = c(rep("Belongingness", length(dvs)),
                                rep("SelfEsteem", length(dvs)),
                                rep("Control", length(dvs)),
                                rep("MeaningfulExistence", length(dvs))),
                       "DV" = c(dvs,dvs,dvs,dvs),
                       "beta" = c(betas1, betas2,betas3,betas4),
                       "se" = c(se1, se2,se3,se4))
  coef_df = coef_df
  return(coef_df)
}
```

## Functional ROIS

```{r}
dvs = c("subacc_roi_mask","rInsula_roi_mask",
        "lInsula_roi_mask", "functional_combined_roi_mask")

coef_df = construct_coef_df_nts(dvs, df) %>%
  mutate(DV = gsub("_roi_mask", "", DV))
plot_coef_iri(coef_dv)
```

## Dufour mentalzing meta-analytic ROIS

```{r}
dvs = c("vmpfc_roi_mask","dmpfc_roi_mask","mmpfc_roi_mask", "precuneus_roi_mask",            "lTpj_roi_mask","rTpj_roi_mask" ,"rSts_roi_mask",
        "saxe_combined_mask")
coef_df = construct_coef_df_nts(dvs, df) %>%
  mutate(DV = gsub("_roi_mask", "", DV))
plot_coef_iri(coef_dv)
```

## Vijayakumar social exclusion meta-analytic ROIs


```{r}
dvs = c("adult_lIFG_mask","adult_vACC_mask",
        "adult_posteriorCingulate_mask","adult_precuneus_mask",
        "adult_precentralGyrus_mask" ,
        "ado_lateralOFC_mask", "ado_vs_mask")

coef_df = construct_coef_df_nts(dvs, df) %>%
  mutate(DV = gsub("_mask", "", DV))
plot_coef_iri(coef_dv)
```

## dACC ROIS

```{r}
dvs = c("rotge_dacc1_mask","rotge_dacc2_mask",
        "dACC_anatomical")

coef_df = construct_coef_df_nts(dvs, df) %>%
  mutate(DV = gsub("_mask", "", DV))
plot_coef_iri(coef_dv)
```

