---
title: "FB use analysis update"
author: '[Rui Pei](https://www.asc.upenn.edu/people/rui-pei)'
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---
```{r setup, warning=TRUE}
rm(list = ls())

if (!require("pacman")) install.packages("pacman",repos = "http://cran.us.r-project.org")
pacman::p_load(ggplot2,ggpubr,tidyverse,plyr, dplyr, knitr, kableExtra, jtools,pander)

source("~/Documents/GitHub/facebookUse/functions.R")
pd <- position_dodge(0.3) # move them .05 to the left and right
```


```{r importWideData, warning = FALSE, message = FALSE}
path =  "/Users/Rui/Box Sync/CurrentProjects_Penn/TPS12_BART/99_fomo/github (peirui@upenn.edu)/"
setwd(path)
## socialMedia data
socialMedia = read.csv(paste0(path, '0_facebook/tps2_facebook.csv'),na.strings=c("","NA"), stringsAsFactors = FALSE)[-1,]

socialMedia = socialMedia %>% 
  mutate(TPS_ID = as.factor(TPS_ID),
         OpenF = as.factor(OpenF)) %>%
  mutate_if(is.character,as.numeric) %>%
  mutate(fhab = rowMeans(.[,10:19], na.rm = FALSE),
         femo = rowMeans(.[c(8,9,20:39)], na.rm = FALSE),
         fconnected = rowMeans(.[c(8,9)], na.rm = FALSE),
         femopost = rowMeans(.[c(20:39)], na.rm = FALSE),
         TPS_ID = as.character(TPS_ID),
         OpenF = as.character(OpenF)) %>%
  drop_na(femo, fhab) %>%
  select(TPS_ID, fhab, femo,fconnected,femopost,ConnFri_2,ConnFam_2, OpenF,
         HabF_1, HabF_2, HabF_3, HabF_4, HabF_5, HabF_6, HabF_7, HabF_8, HabF_9,HabF_10)
  



cyber = read.csv(paste0(path, '0_cyberball/cyberball_roi.csv'), stringsAsFactors = FALSE) 

age = read.csv(paste0(path, '0_surveys/demo.csv'), stringsAsFactors = FALSE) %>%
  select(TPS_ID, age, study_t, scanner_t)

iri = read.csv(paste0(path, '0_surveys/iri_tps12.csv'), stringsAsFactors = FALSE)
iri = iri %>%
  mutate(IRI_mean = rowMeans(select(iri, starts_with("IRI_")), na.rm = FALSE))


nts = read.csv(paste0(path, '0_surveys/nts.csv'), stringsAsFactors = FALSE)

df = cyber %>%
  left_join(socialMedia, by = "TPS_ID") %>%
  left_join(age, by = "TPS_ID") %>%
  left_join(iri, by = "TPS_ID") %>%
  left_join(nts, by = "TPS_ID") 

# Remove NAs
df = df %>% drop_na(fhab,femo, NTS_Belongingness,
                    NTS_SelfEsteem, NTS_Control,
                    NTS_MeaningfulExistence, study_t, scanner_t,
                    IRI_Perspective_Taking, IRI_Fantasy, 
                    IRI_Empathic_Concern, IRI_Personal_Distress,
                    fconnected) %>% 
  mutate(NTS_Belongingness = 7 - NTS_Belongingness,
         NTS_SelfEsteem = 7 - NTS_SelfEsteem,
         NTS_Control = 7 - NTS_Control,
         NTS_MeaningfulExistence = 7 - NTS_MeaningfulExistence,
         NTS_Mean = 7 - NTS_Mean)


```


# Method 

Participant age

```{r}
tps1 = df %>% filter( study_t == "tps1")
tps2 = df %>% filter( study_t == "tps2")
round(mean(df$age),2)
round(sd(df$age),2)

round(mean(tps1$age),2)
round(sd(tps1$age),2)

round(mean(tps2$age),2)
round(sd(tps2$age),2)

t.test(tps1$age, tps2$age)
```

## Facebook measures

```{r}
cor.test(socialMedia$ConnFam_2, socialMedia$ConnFri_2, method = "pearson")
psych::alpha(socialMedia %>% select(ConnFam_2, ConnFri_2))
```



## Check normal distribution

__Dar's comment:__
Yeah, I actually really don't put much credit into the shapiro-wilk test because it's too sentisitive, same with the kolmogorov-smirnov. You can plot our histograms and see clear gaussian distributions but the data will still fail these tests. What I do is figure out the skewness and kurtosis and the standard error for each of these as well. I then divide the skewness by the SE of skewness and it needs to be between +/-3. I then divide the kurtosis by the SE kurtosis and it needs to be between +/-3 as well. Alternately your actual skewness can be between +/-2 and kurtosis +/-9. See Schmider, Ziegler, Danay, Beyer & Buhner, 2010.

```{r message = FALSE,warning = FALSE}
stat1 = spssSkewKurtosis(df$fhab)[1,2]/spssSkewKurtosis(df$fhab)[1,1]
g1 = gghistogram(df$fhab, title = "Habitual FB use") + 
  annotate("text", x=6, y=5, label= paste("stat = ", round(stat1,2)))
round(mean(df$fhab),2)
round(sd(df$fhab),2)

stat2 = spssSkewKurtosis(df$fconnected)[1,2]/spssSkewKurtosis(df$fconnected)[1,1]
g2 = gghistogram(df$fconnected, title = "FB connectedness") + 
  annotate("text", x=4, y=10, label= paste("stat = ", round(stat2,2)))
round(mean(df$fconnected),2)
round(sd(df$fconnected),2)

stat3 = spssSkewKurtosis(df$IRI_Perspective_Taking)[1,2]/spssSkewKurtosis(df$IRI_Perspective_Taking)[1,1]
g3 = gghistogram(df$IRI_Perspective_Taking, title = "Perspective taking") + 
  annotate("text", x=15, y=5, label= paste("stat = ", round(stat3,2)))

stat4 = spssSkewKurtosis(df$NTS_Mean)[1,2]/spssSkewKurtosis(df$NTS_Mean)[1,1]
g4 = gghistogram(df$NTS_Mean, title = "NTS") + 
  annotate("text", x=1.5, y=4, label= paste("stat = ", round(stat3,2)))

multiplot(g1,g3,g2,g4, cols=2)

```

```{r}
md1 = lm(fconnected ~ fhab +study_t+ age, data = df)
summ(md1, vifs = TRUE,confint = TRUE, ci.width = 0.95)
ggscatter(df, "fhab", "fconnected")
```



# Results

## 1 Facebook use measures

```{r}
round(mean(df$fconnected),2)
round(sd(df$fconnected),2)
round(mean(df$fhab),2)
round(sd(df$fhab),2)

md = lm( fconnected~ fhab + age + study_t, data = df)
summ(md, confint = T, scale = F)
```

## 2 Connectedness on Facebook and neural responses to social exclusion

```{r}
md = lm(ado_rois_mask~ fconnected+ scanner_t + study_t + age , data = df)
summ(md, confint = T, scale = F)
md = lm(ado_vs_mask~ fconnected+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)
md = lm(ado_lateralOFC_mask~ fconnected+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)


md = lm(saxe_combined_mask~ fconnected+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)


md = lm(ado_rois_mask~ ConnFri_2+ scanner_t + study_t + age , data = df)
summ(md, confint = T, scale = F)
md = lm(ado_vs_mask~ ConnFri_2+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)
md = lm(ado_lateralOFC_mask~ ConnFri_2+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)
md = lm(saxe_combined_mask~ ConnFri_2+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)
md = lm(NTS_Mean~ ConnFri_2+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)

md = lm(ado_rois_mask~ ConnFam_2+ scanner_t + study_t + age , data = df)
summ(md, confint = T, scale = F)
md = lm(ado_vs_mask~ ConnFam_2+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)
md = lm(ado_lateralOFC_mask~ ConnFam_2+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)
md = lm(saxe_combined_mask~ ConnFam_2+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)
md = lm(NTS_Mean~ ConnFam_2+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)
```

## 3 Habitual use of Facebook and neural responses to social exclusion

```{r}
md = lm(ado_rois_mask~ fhab+ scanner_t + study_t + age , data = df)
summ(md, confint = T, scale = F)
md = lm(ado_vs_mask~ fhab+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)
md = lm(ado_lateralOFC_mask~ fhab+ scanner_t + study_t + age, data = df)
summ(md, confint = T, scale = F)


md = lm(saxe_combined_mask~ fhab+ scanner_t + study_t + age, data = df)
summ(md, confint = T, digits = 3,scale = F)
md = lm(dmpfc_roi_mask~ fhab+ scanner_t + study_t + age, data = df)
summ(md, confint = T, digits = 2,scale = F)
md = lm(mmpfc_roi_mask~ fhab+ scanner_t + study_t + age, data = df)
summ(md, confint = T, digits = 2,scale = F)
md = lm(lTpj_roi_mask~ fhab+ scanner_t + study_t + age, data = df)
summ(md, confint = T, digits = 2,scale = F)
md = lm(rTpj_roi_mask~ fhab+ scanner_t + study_t + age, data = df)
summ(md, confint = T, digits = 3,scale = F)

```
4. Facebook use and NTS

```{r}
md1 = lm(NTS_Mean ~ fconnected +study_t +age, data = df)
summ(md1, vifs = TRUE,confint = TRUE, ci.width = 0.95)

md2 = lm(NTS_Mean ~ fhab +study_t +age, data = df)
summ(md2, vifs = TRUE,confint = TRUE, ci.width = 0.95)



md1 = lm(NTS_Mean ~ saxe_combined_mask +study_t + scanner_t +age, data = df)
summ(md1, vifs = TRUE,confint = TRUE, ci.width = 0.95)

md1 = lm(NTS_Mean ~ ado_rois_mask +study_t + scanner_t + age, data = df)
summ(md1, vifs = TRUE,confint = TRUE, ci.width = 0.95)
```

# Tables

## Table 2
 fconnected predicting social pain ROIs

```{r}
md5.1 = lm(ado_vs_mask ~ fconnected +study_t +scanner_t + age, data = df)
md5.2 = lm(ado_lateralOFC_mask ~ fconnected +study_t +scanner_t + age, data = df)
export_summs(md5.1, md5.2,scale = FALSE,
              error_format = "[{conf.low}, {conf.high}]",
             to.file = "xlsx", file.name = "table3.xlsx")
summary(md5.1)
```
## Table 3
 fconnected predicting mentalizing ROIs

```{r}
md3.1 = lm(dmpfc_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.1 = summ(md3.1, vifs = FALSE,confint = TRUE, ci.width = 0.95, digits = 2)
md3.2 = lm(mmpfc_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.2 = summ(md3.2, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.3 = lm(vmpfc_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.3 = summ(md3.3 , vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.4 = lm(precuneus_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.4 = summ(md3.4, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.5 = lm(lTpj_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.5 = summ(md3.5, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.6 = lm(rTpj_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.6 = summ(md3.6, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.7 = lm(rSts_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.7 = summ(md3.7, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)



export_summs(md3.1, md3.2, md3.3, md3.4, md3.5,md3.6, md3.7,scale = FALSE,
              error_format = "[{conf.low}, {conf.high}]",
            to.file = "xlsx", file.name = "table2.xlsx")
```

## Table 3
 fhab predicting social pain ROIs

```{r}
md5.1 = lm(ado_vs_mask ~ fhab +study_t +scanner_t + age, data = df)
md5.2 = lm(ado_lateralOFC_mask ~ fhab +study_t +scanner_t + age, data = df)
export_summs(md5.1, md5.2,scale = FALSE,
              error_format = "[{conf.low}, {conf.high}]",
             to.file = "xlsx", file.name = "table3.xlsx")
```

## Table 4
 fconnected predicting mentalizing ROIs

```{r}
md3.1 = lm(dmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.1 = summ(md3.1, vifs = FALSE,confint = TRUE, ci.width = 0.95, digits = 2)
md3.2 = lm(mmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.2 = summ(md3.2, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.3 = lm(vmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.3 = summ(md3.3 , vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.4 = lm(precuneus_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.4 = summ(md3.4, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.5 = lm(lTpj_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.5 = summ(md3.5, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.6 = lm(rTpj_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.6 = summ(md3.6, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.7 = lm(rSts_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.7 = summ(md3.7, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)



export_summs(md3.1, md3.2, md3.3, md3.4, md3.5,md3.6, md3.7,scale = FALSE,
              error_format = "[{conf.low}, {conf.high}]",
             to.file = "xlsx", file.name = "table4.xlsx")
```