---
title: "FB use analysis update"
author: '[Rui Pei](https://www.asc.upenn.edu/people/rui-pei)'
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---
```{r setup, warning=TRUE}
rm(list = ls())

if (!require("pacman")) install.packages("pacman",repos = "http://cran.us.r-project.org")
pacman::p_load(ggplot2,ggpubr,tidyverse,plyr, dplyr, knitr, kableExtra, jtools,pander)

source("~/Documents/GitHub/facebookUse/functions.R")
pd <- position_dodge(0.3) # move them .05 to the left and right
```


```{r importWideData, warning = FALSE, message = FALSE}
path =  "/Users/Rui/Box Sync/CurrentProjects_Penn/TPS12_BART/99_fomo/github (peirui@upenn.edu)/"
setwd(path)
## socialMedia data
socialMedia = read.csv(paste0(path, '0_facebook/tps2_facebook.csv'),na.strings=c("","NA"), stringsAsFactors = FALSE)[-1,]

socialMedia = socialMedia %>% 
  mutate(TPS_ID = as.factor(TPS_ID),
         OpenF = as.factor(OpenF)) %>%
  mutate_if(is.character,as.numeric) %>%
  mutate(fhab = rowMeans(.[,10:19], na.rm = FALSE),
         femo = rowMeans(.[c(8,9,20:39)], na.rm = FALSE),
         fconnected = rowMeans(.[c(8,9)], na.rm = FALSE),
         femopost = rowMeans(.[c(20:39)], na.rm = FALSE),
         TPS_ID = as.character(TPS_ID),
         OpenF = as.character(OpenF)) %>%
  select(TPS_ID, fhab, femo,fconnected,femopost,ConnFri_2,ConnFam_2, OpenF)
  



cyber = read.csv(paste0(path, '0_cyberball/cyberball_roi.csv'), stringsAsFactors = FALSE) 

age = read.csv(paste0(path, '0_surveys/demo.csv'), stringsAsFactors = FALSE) %>%
  select(TPS_ID, age, study_t, scanner_t)

iri = read.csv(paste0(path, '0_surveys/iri_tps12.csv'), stringsAsFactors = FALSE)
iri = iri %>%
  mutate(IRI_mean = rowMeans(select(iri, starts_with("IRI_")), na.rm = FALSE))


nts = read.csv(paste0(path, '0_surveys/nts.csv'), stringsAsFactors = FALSE)

df = cyber %>%
  left_join(socialMedia, by = "TPS_ID") %>%
  left_join(age, by = "TPS_ID") %>%
  left_join(iri, by = "TPS_ID") %>%
  left_join(nts, by = "TPS_ID") 

# Remove NAs
df = df %>% drop_na(fhab,femo, NTS_Belongingness,
                    NTS_SelfEsteem, NTS_Control,
                    NTS_MeaningfulExistence, study_t, scanner_t,
                    IRI_Perspective_Taking, IRI_Fantasy, 
                    IRI_Empathic_Concern, IRI_Personal_Distress,
                    fconnected) %>% 
  mutate(NTS_Belongingness = 7 - NTS_Belongingness,
         NTS_SelfEsteem = 7 - NTS_SelfEsteem,
         NTS_Control = 7 - NTS_Control,
         NTS_MeaningfulExistence = 7 - NTS_MeaningfulExistence,
         NTS_Mean = 7 - NTS_Mean)
```


# Method 

Participant age

```{r}
tps1 = df %>% filter( study_t == "tps1")
tps2 = df %>% filter( study_t == "tps2")
round(mean(df$age),2)
round(sd(df$age),2)

round(mean(tps1$age),2)
round(sd(tps1$age),2)

round(mean(tps2$age),2)
round(sd(tps2$age),2)

t.test(tps1$age, tps2$age)
```

## Check normal distribution

__Dar's comment:__
Yeah, I actually really don't put much credit into the shapiro-wilk test because it's too sentisitive, same with the kolmogorov-smirnov. You can plot our histograms and see clear gaussian distributions but the data will still fail these tests. What I do is figure out the skewness and kurtosis and the standard error for each of these as well. I then divide the skewness by the SE of skewness and it needs to be between +/-3. I then divide the kurtosis by the SE kurtosis and it needs to be between +/-3 as well. Alternately your actual skewness can be between +/-2 and kurtosis +/-9. See Schmider, Ziegler, Danay, Beyer & Buhner, 2010.

```{r message = FALSE,warning = FALSE}
stat1 = spssSkewKurtosis(df$fhab)[1,2]/spssSkewKurtosis(df$fhab)[1,1]
g1 = gghistogram(df$fhab, title = "Habitual FB use") + 
  annotate("text", x=6, y=5, label= paste("stat = ", round(stat1,2)))
round(mean(df$fhab),2)
round(sd(df$fhab),2)

stat2 = spssSkewKurtosis(df$fconnected)[1,2]/spssSkewKurtosis(df$fconnected)[1,1]
g2 = gghistogram(df$fconnected, title = "FB connectedness") + 
  annotate("text", x=4, y=10, label= paste("stat = ", round(stat2,2)))
round(mean(df$fconnected),2)
round(sd(df$fconnected),2)

stat3 = spssSkewKurtosis(df$IRI_Perspective_Taking)[1,2]/spssSkewKurtosis(df$IRI_Perspective_Taking)[1,1]
g3 = gghistogram(df$IRI_Perspective_Taking, title = "Perspective taking") + 
  annotate("text", x=15, y=5, label= paste("stat = ", round(stat3,2)))

stat4 = spssSkewKurtosis(df$NTS_Mean)[1,2]/spssSkewKurtosis(df$NTS_Mean)[1,1]
g4 = gghistogram(df$NTS_Mean, title = "NTS") + 
  annotate("text", x=1.5, y=4, label= paste("stat = ", round(stat3,2)))

multiplot(g1,g3,g2,g4, cols=2)

```

```{r}
md1 = lm(fconnected ~ fhab +study_t+ age, data = df)
summ(md1, vifs = TRUE,confint = TRUE, ci.width = 0.95)
ggscatter(df, "fhab", "fconnected")
```



# Results

## 3.1 Facebook use measures

## 3.2 2 Neural responses to social exclusion and self-reported psychological distress

## 3.3 Habitual Facebook use and neural responses to social exclusion

```{r}
md1 = lm(saxe_combined_mask ~ fhab +study_t + scanner_t + age, data = df)
summ(md1, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)

md1.1 = lm(dmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum1.1 = summ(md1.1, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md1.2 = lm(mmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum1.2 = summ(md1.2, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md1.3 = lm(vmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum1.3 = summ(md1.3 , vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md1.4 = lm(precuneus_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum1.4 = summ(md1.4, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md1.5 = lm(lTpj_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum1.5 = summ(md1.5, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md1.6 = lm(rTpj_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum1.6 = summ(md1.6, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md1.7 = lm(rSts_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum1.7 = summ(md1.7, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
```

```{r}
md2 = lm(ado_rois_mask ~ fhab +study_t + scanner_t + age, data = df)
summ(md2, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)

md2.1 = lm(ado_lateralOFC_mask ~ fhab +study_t + scanner_t + age, data = df)
sum2.1 = summ(md2.1, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md2.2 = lm(ado_vs_mask ~ fhab +study_t + scanner_t + age, data = df)
sum2.2 = summ(md2.2, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
```

## 3.4  Facebook connectedness and neural responses to social exclusion

```{r}
md3 = lm(saxe_combined_mask ~ fconnected +study_t + scanner_t + age, data = df)
summ(md3, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)

md3.1 = lm(dmpfc_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.1 = summ(md3.1, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.2 = lm(mmpfc_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.2 = summ(md3.2, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.3 = lm(vmpfc_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.3 = summ(md3.3 , vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.4 = lm(precuneus_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.4 = summ(md3.4, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.5 = lm(lTpj_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.5 = summ(md3.5, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.6 = lm(rTpj_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.6 = summ(md3.6, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.7 = lm(rSts_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.7 = summ(md3.7, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
```

```{r}
md4 = lm(ado_rois_mask ~ fconnected +study_t + scanner_t + age, data = df)
summ(md4, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)

md4.1 = lm(ado_lateralOFC_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum4.1 = summ(md4.1, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md4.2 = lm(ado_vs_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum4.2 = summ(md4.2, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)

ps = c(sum1.1$coeftable[2,5],sum1.2$coeftable[2,5],sum1.3$coeftable[2,5],sum1.4$coeftable[2,5],
      sum1.5$coeftable[2,5],sum1.6$coeftable[2,5],sum1.7$coeftable[2,5],
      sum2.1$coeftable[2,5],sum2.2$coeftable[2,5],
      sum3.1$coeftable[2,5],sum3.2$coeftable[2,5],sum3.3$coeftable[2,5],sum3.4$coeftable[2,5],
      sum3.5$coeftable[2,5],sum3.6$coeftable[2,5],sum3.7$coeftable[2,5],
      sum4.1$coeftable[2,5],sum4.2$coeftable[2,5])
ps_adj = p.adjust(ps,method = "BH")
which(ps < 0.05)
```


```{r}
md2 = lm(NTS_Mean ~ fhab +study_t +age, data = df)
summ(md2, vifs = TRUE,confint = TRUE, ci.width = 0.95)

md1 = lm(NTS_Mean ~ fconnected +study_t +age, data = df)
summ(md1, vifs = TRUE,confint = TRUE, ci.width = 0.95)

md1 = lm(NTS_Mean ~ saxe_combined_mask +study_t + scanner_t +age, data = df)
summ(md1, vifs = TRUE,confint = TRUE, ci.width = 0.95)

md1 = lm(NTS_Mean ~ ado_rois_mask +study_t + scanner_t + age, data = df)
summ(md1, vifs = TRUE,confint = TRUE, ci.width = 0.95)


dvs = c("NTS_Belongingness" ,"NTS_SelfEsteem","NTS_Control",
        "NTS_MeaningfulExistence","NTS_Mean")
coef_df = construct_coef_df(dvs, df) 
plot_coef_df(coef_dv)
```



## 3.2 Facebook measures and perspective taking

```{r}
md3 = lm(IRI_Perspective_Taking ~ fconnected + study_t +scanner_t + age, data = df)
summ(md3, vifs = TRUE,confint = TRUE, ci.width = 0.95)
md4 = lm(IRI_Perspective_Taking ~ fhab+ study_t +scanner_t + age , data = df)
summ(md4, vifs = TRUE,confint = TRUE, ci.width = 0.95)
md3.1 = lm(IRI_Fantasy ~ fhab  +study_t +scanner_t+age , data = df)
summ(md3.1, vifs = TRUE,confint = TRUE, ci.width = 0.95)
ggscatter(df, "fhab", "fconnected")

dvs = c("IRI_Perspective_Taking", "IRI_Fantasy",
        "IRI_Empathic_Concern", "IRI_Personal_Distress" , "IRI_mean")
coef_df = construct_coef_df(dvs, df) 
plot_coef_df(coef_dv)
colnames(df)
```


```{r}
md5 = lm(ado_rois_mask ~ fconnected + study_t +scanner_t + age, data = df)
summ(md5, vifs = TRUE,confint = TRUE, ci.width = 0.95)

md5 = lm(ado_lateralOFC_mask ~ fconnected +study_t +scanner_t + age, data = df)
summ(md5, vifs = TRUE,confint = TRUE, ci.width = 0.95)

md5 = lm(ado_vs_mask ~ fconnected +study_t +scanner_t + age, data = df)
summ(md5, vifs = TRUE,confint = TRUE, ci.width = 0.95)


md5 = lm(ado_lateralOFC_mask ~ fhab +study_t +scanner_t + age, data = df)
summ(md5, vifs = TRUE,confint = TRUE, ci.width = 0.95)


```

## 3.4 Facebook measures and mentalizing activity

```{r}
md5 = lm(saxe_combined_mask ~ fconnected + study_t+scanner_t , data = df)
summ(md5, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 2)
md5 = lm(saxe_combined_mask ~ fhab +study_t +scanner_t + age, data = df)
summ(md5, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
ggscatter(df, "fhab","saxe_combined_mask")

```

```{r}
dvs = c("NTS_Mean", "IRI_Perspective_Taking", "IRI_Fantasy")

coef_df = construct_coef_df(dvs, df) %>%
  filter(IV != "Emotional FB use")
g1 = plot_coef_df(coef_dv)+ coord_flip()

dvs = c("ado_vs_mask", "ado_lateralOFC_mask", "saxe_combined_mask")

coef_df = construct_coef_df(dvs, df) %>%
  filter(IV != "Emotional FB use")
g2 = plot_coef_df(coef_dv) + coord_flip()

multiplot(g1, g2, cols = 1)
```

# Word cloud

```{r}
pacman::p_load(SnowballC, wordcloud,
               RColorBrewer,wordcloud2)
## Habitual FB use 
df$fhab_s = scale(df$fhab)
total_wc = getWC_mat(df$OpenF[1], df$fhab_s[1])
colnames(total_wc)[2] = "col1"
for (i in c(2:dim(df)[1])){
  wc = getWC_mat(df$OpenF[i], df$fhab_s[i])
  colnames(wc)[2] = paste0("col",i)
  total_wc = merge(total_wc, wc, by = "word", all = TRUE)
}

total_wc$freq = rowMeans(total_wc %>% select(-word), na.rm = TRUE)

## FB connectedness
df$fconnected_s = scale(df$fconnected)
total_wc2 = getWC_mat(df$OpenF[1], df$fconnected_s[1])
colnames(total_wc2)[2] = "col1"
for (i in c(2:dim(df)[1])){
  wc = getWC_mat(df$OpenF[i], df$fconnected_s[i])
  colnames(wc)[2] = paste0("col",i)
  total_wc2 = merge(total_wc2, wc, by = "word", all = TRUE)
}

total_wc2$freq = rowMeans(total_wc2 %>% select(-word), 
                          na.rm = TRUE)


# 
# 
# wordcloud2(data=total_wc %>% select(word,freq), 
#            size = 0.7, shape = 'rectangle',
#            minRotation = 0, maxRotation = 0, rotateRatio = 1,
#            hoverFunction = FALSE)
# 
# wordcloud2(data=total_wc2 %>% select(word,freq), 
#            size = 0.7, shape = 'rectangle',
#            minRotation = 0, maxRotation = 0, rotateRatio = 1)

```


# Figures 

## Figure 1

```{r}
f1.0 = lm(ado_vs_mask ~ study_t + scanner_t + age, data = df)
f1.1 = lm(ado_vs_mask ~ fconnected +study_t + scanner_t+age, data = df)
f1.3 = lm(NTS_Mean ~ fconnected +study_t +age, data = df)
summ(f1.3, digits = 2, confint = TRUE)
f1.3 = lm(NTS_Mean ~ fhab +study_t +age, data = df)
summ(f1.3, digits = 2, confint = TRUE)
df$ado_vs_mask_resid = f1.0$residuals


f2.0 = lm(ado_lateralOFC_mask ~ study_t + scanner_t + age, data = df)
f2.1 = lm(ado_lateralOFC_mask ~ fconnected +study_t + scanner_t + age, data = df)
df$ado_lateralOFC_mask_resid = f2.0$residuals
summ(f2.1, digits = 2, confint = TRUE)

ggscatter(df, "fconnected", "ado_vs_mask_resid",
          color = "#003C67FF",
          size = 3, alpha = 0.6,
          add = "reg.line",
          add.params = list(color = "#003C67FF", fill = "#7AA6DCFF"), 
   conf.int = TRUE) + xlab("") + ylab("")

ggscatter(df, "fconnected", "ado_lateralOFC_mask_resid",
          color = "#A73030FF",
          size = 3, alpha = 0.6,
          add = "reg.line",
          add.params = list(color = "#A73030FF", fill = "#CD534CFF"), 
   conf.int = TRUE)+ xlab("") + ylab("")

```

## Figure 2

```{r}
f3.0 = lm(saxe_combined_mask ~ study_t + scanner_t + age, data = df)
f3.1 = lm(saxe_combined_mask ~ fhab +study_t + scanner_t +age, data = df)

summ(f3.1, digits = 3, confint = TRUE)
df$saxe_combined_mask_resid = f3.0$residuals

f4.0 = lm(dmpfc_roi_mask ~ study_t + scanner_t + age, data = df)
f4.1 = lm(dmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
df$dmpfc_roi_mask_resid = f4.0$residuals
summ(f4.1, digits = 2, confint = TRUE)

f5.0 = lm(lTpj_roi_mask ~ study_t + scanner_t + age, data = df)
f5.1 = lm(lTpj_roi_mask~ fhab +study_t + scanner_t + age, data = df)
df$lTpj_roi_mask_resid = f5.0$residuals
summ(f5.1, digits = 2, confint = TRUE)


f6.0 = lm(rTpj_roi_mask ~ study_t + scanner_t + age, data = df)
f6.1 = lm(rTpj_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
df$rTpj_roi_mask_resid = f6.0$residuals
summ(f6.1, digits = 3, confint = TRUE)


f7.0 = lm(mmpfc_roi_mask ~ study_t + scanner_t + age, data = df)
f7.1 = lm(mmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
df$mmpfc_roi_mask_resid = f7.0$residuals
summ(f7.1, digits = 2, confint = TRUE)

ggscatter(df, "fhab", "saxe_combined_mask_resid",
          color = "#767676FF",
          size = 3, alpha = 0.6,
          add = "reg.line",
          add.params = list(color = "#3F4041FF", fill = "#767676FF"), 
   conf.int = TRUE) + xlab("") + ylab("")


ggscatter(df, "fhab", "dmpfc_roi_mask_resid",
          color = "#20854ECC",
          size = 3, alpha = 0.6,
          add = "reg.line",
          add.params = list(color = "#20854EFF", fill = "#20854ECC"), 
   conf.int = TRUE) + xlab("") + ylab("")

ggscatter(df, "fhab", "mmpfc_roi_mask_resid",
          color = "#BB0021B2",
          size = 3, alpha = 0.6,
          add = "reg.line",
          add.params = list(color = "#BB0021FF", fill = "#BB0021B2"), 
   conf.int = TRUE) + xlab("") + ylab("")

ggscatter(df, "fhab", "lTpj_roi_mask_resid",
          color = "#E18727CC",
          size = 3, alpha = 0.6,
          add = "reg.line",
          add.params = list(color = "#E18727FF", fill = "#E18727CC"), 
   conf.int = TRUE) + xlab("") + ylab("")

ggscatter(df, "fhab", "rTpj_roi_mask_resid",
          color = "#631879B2",
          size = 3, 
          add = "reg.line",
          add.params = list(color = "#631879FF", fill = "#631879B2"), 
   conf.int = TRUE) + xlab("") + ylab("")

library(scales)
library(ggsci)
show_col(pal_aaas("default")(10))
show_col(pal_aaas("default", alpha = 0.7)(10))
```


# Tables


## Table 2
 fconnected predicting mentalizing ROIs

```{r}
md3.1 = lm(dmpfc_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.1 = summ(md3.1, vifs = FALSE,confint = TRUE, ci.width = 0.95, digits = 2)
md3.2 = lm(mmpfc_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.2 = summ(md3.2, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.3 = lm(vmpfc_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.3 = summ(md3.3 , vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.4 = lm(precuneus_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.4 = summ(md3.4, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.5 = lm(lTpj_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.5 = summ(md3.5, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.6 = lm(rTpj_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.6 = summ(md3.6, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.7 = lm(rSts_roi_mask ~ fconnected +study_t + scanner_t + age, data = df)
sum3.7 = summ(md3.7, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)



export_summs(md3.1, md3.2, md3.3, md3.4, md3.5,md3.6, md3.7,scale = FALSE,
              error_format = "[{conf.low}, {conf.high}]",
             to.file = "xlsx", file.name = "table2.xlsx")
```

## Table 3
 fhab predicting social pain ROIs

```{r}
md5.1 = lm(ado_vs_mask ~ fhab +study_t +scanner_t + age, data = df)
md5.2 = lm(ado_lateralOFC_mask ~ fhab +study_t +scanner_t + age, data = df)
export_summs(md5.1, md5.2,scale = FALSE,
              error_format = "[{conf.low}, {conf.high}]",
             to.file = "xlsx", file.name = "table3.xlsx")
```

## Table 4
 fconnected predicting mentalizing ROIs

```{r}
md3.1 = lm(dmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.1 = summ(md3.1, vifs = FALSE,confint = TRUE, ci.width = 0.95, digits = 2)
md3.2 = lm(mmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.2 = summ(md3.2, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.3 = lm(vmpfc_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.3 = summ(md3.3 , vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.4 = lm(precuneus_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.4 = summ(md3.4, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.5 = lm(lTpj_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.5 = summ(md3.5, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.6 = lm(rTpj_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.6 = summ(md3.6, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)
md3.7 = lm(rSts_roi_mask ~ fhab +study_t + scanner_t + age, data = df)
sum3.7 = summ(md3.7, vifs = TRUE,confint = TRUE, ci.width = 0.95, digits = 3)



export_summs(md3.1, md3.2, md3.3, md3.4, md3.5,md3.6, md3.7,scale = FALSE,
              error_format = "[{conf.low}, {conf.high}]",
             to.file = "xlsx", file.name = "table4.xlsx")
```